Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-04 Geometric types.tex
Swap 4.1 and 4.2

\subsection{Equivariance Weil sheaf complexes (move to somewhere else?)}\label{ssec:equivariant}

@@

If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
Suppose that
\begin{enumerate}
\labitem{(Lang.1)}{Lang.1} $G(k) \subset \image(L)$ (which will hold if $G$ is connected).
\end{enumerate}
Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
If $x \in G(k)$, write $x = L(y)$ and define $\tilde{\chi}(x) = \chi(\tilde{L}(y))$.
Note that $\tilde{\chi}$ is well defined since changing $y$ to $gy$ for $g \in G(k)$ has the
effect of conjugating $\tilde{L}(y)$ by $g$, which has no effect on the value $\chi(\tilde{L}(y))$.
Then we must also assume that
\begin{enumerate}
\labitem{(Lang.2)}{Lang.2} $\tilde{\chi}$ is also a character.
\end{enumerate}

>>>>

If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
Suppose that
\begin{enumerate}
\labitem{(L.1)}{L.1} $G(k) \subset \image(L)$ (which will hold if $G$ is connected).
\end{enumerate}
Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
If $x \in G(k)$, write $x = L(y)$ and define $\tilde{\chi}(x) = \chi(\tilde{L}(y))$.
Note that $\tilde{\chi}$ is well defined since changing $y$ to $gy$ for $g \in G(k)$ has the
effect of conjugating $\tilde{L}(y)$ by $g$, which has no effect on the value $\chi(\tilde{L}(y))$.
Then we must also assume that
\begin{enumerate}
\labitem{(L.2)}{L.2} $\tilde{\chi}$ is also a character.
\end{enumerate}

\subsection{Equivariant Weil sheaf complexes}\label{ssec:equivariant}

@@
